---
title: "Using GitHub for Collaboration"
author: "Hao Ye"
institute: "Health Science Center Libraries, University of Florida"
date: "(updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    seal: false
    fig_caption: false
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#09274B",
  base_font_size = "32px", 
  header_h1_font_size = "2.0rem",
  header_h2_font_size = "1.5rem",
  header_h3_font_size = "1.25rem", 
  header_background_content_padding_top = "2rem", 
  header_font_google = google_font("Lato"),
  text_font_google   = google_font("Montserrat", "300", "300i", "500"),
  code_font_google   = google_font("Source Code Pro", "300", "500"), 
  extra_css = list("p" = list("margin-block-start" = "0.5em", 
                              "margin-block-end" = "0.5em"), 
                   "ul" = list("margin-block-start" = "0.5em", 
                              "margin-block-end" = "0.5em"), 
                   "li" = list("margin-block-start" = "0.5em", 
                              "margin-block-end" = "0.5em"), 
                   "pre" = list("margin-top" = "0.5em", 
                              "margin-bottom" = "0.5em"), 
                   ".caption" = list("display" = "none")), 
  link_color = "#339944"
)
```
class: inverse, center, middle

# `r rmarkdown::metadata$title`
### `r rmarkdown::metadata$author`
### `r rmarkdown::metadata$institute`
### (updated: `r Sys.Date()`)

---

# Motivations

* One of the most powerful advantages for using version control is managing collaborative work.
* Git is a flexible tool that accommodates many different styles of collaboration...
* "GitHub flow" is a lightweight workflow that scales well for small research teams and is not too complex

---

# Learning Outcomes

* describe how merge conflicts originate and how to resolve them
* create and navigate branches on GitHub and using GitHub Desktop
* create and resolve issues
* create and merge pull requests
* apply the "GitHub flow" workflow for collaborating
* understand "forks" and open-source-community development on GitHub
---

class: inverse, center, middle

# 

---

# Thanks

* Let me know what content you'd like to see
* Contact me for additional questions or consultation requests!
* Check back in on the libguide for more modules and contact info:
  - https://guides.uflib.ufl.edu/reproducibility
